No early warning signals for stochastic transitions: insights from large deviation theory

### 2013-07-11 inst/doc/sig-tests.Rmd
significance tests (use correct one-sided test)

```{r}
x <- subset(dat, variable=="Autocorrelation" & data=="null" & model == "OU")$value
y <- subset(dat, variable=="Autocorrelation" & data=="conditional" & model == "OU")$value
wilcox.test(x,y, alternative="greater")
ks.test(x,y, alternative="greater")
```

@@

```{r}
x <- subset(dat, variable=="Variance" & data=="null" & model == "OU")$value
y <- subset(dat, variable=="Variance" & data=="conditional" & model == "OU")$value
wilcox.test(x,y, alternative="greater")
ks.test(x,y, alternative="greater")
```

@@

```{r}
x <- subset(dat, variable=="Variance" & data=="null" & model == "Allee")$value
y <- subset(dat, variable=="Variance" & data=="conditional" & model == "Allee")$value
wilcox.test(x,y, alternative="greater")
ks.test(x,y, alternative="greater")
```

>>>>

```{r}
x <- subset(dat, variable=="Autocorrelation" & data=="null" & model == "OU")$value
y <- subset(dat, variable=="Autocorrelation" & data=="conditional" & model == "OU")$value
wilcox.test(x,y, alternative="less") # x - y < 0 since y bigger than x
ks.test(x,y, alternative="greater") # CDF x > then CDF y since more weight to the left
```

@@

```{r}
x <- subset(dat, variable=="Variance" & data=="null" & model == "OU")$value
y <- subset(dat, variable=="Variance" & data=="conditional" & model == "OU")$value
wilcox.test(x,y, alternative="less") # x - y < 0 since y bigger than x
ks.test(x,y, alternative="greater") # CDF x > then CDF y since more weight to the left
```

@@

```{r}
x <- subset(dat, variable=="Variance" & data=="null" & model == "Allee")$value
y <- subset(dat, variable=="Variance" & data=="conditional" & model == "Allee")$value
wilcox.test(x,y, alternative="less") # x - y < 0 since y bigger than x
ks.test(x,y, alternative="greater") # CDF x > then CDF y since more weight to the left
```
